---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
Sys.setenv(TZ="Europe/London")
```

# bballR: Scrape basketball data from basketball-reference.com in R

The bballR package uses [tidyverse]("https://www.tidyverse.org/") packages to
efficiently scrape data from 
[basketball-reference]("https://www.basketball-reference.com/") and return it in
the tidy data format.

## Installation

```{r, eval = FALSE}
devtools::install_github("bobbyingram/bballR")
```

## Usage

### Players
To scrape high-level player information for players in the [basketball-reference player database]("https://www.basketball-reference.com/players/") use
```{r}
library(bballR)
players <- scrape_all_players()
dplyr::glimpse(players)
```

### Teams
To scrape high-level information for teams in the the [basketball-reference team database]("https://www.basketball-reference.com/teams/") use
```{r}
all_teams <- scrape_teams()
active_teams <- scrape_teams(status = "active")
defunct_teams <- scrape_teams(status = "defunct")
dplyr::glimpse(all_teams)
```

### Seasons
To scrape summary player performance data for an individual season use
```{r}
season <- 2017
per_game_2017 <- scrape_season_per_game(season)
per_100_2017 <- scrape_season_per_100_poss(season)
per_36_2017 <- scrape_season_per_36_minute(season)
adv_2017 <- scrape_season_advanced(season)
totals_2017 <- scrape_season_totals(season)
dplyr::glimpse(per_game_2017)
```
### Game Logs
To scrape an individual players regular season game logs from a single season 
you need to know use unique player Id from the players lookup:
```{r}
player <- "Dwyane Wade"
wade <- dplyr::filter(players, Player == player)
wade_logs <- scrape_game_logs(wade$PlayerId, season)
dplyr::glimpse(wade_logs)
```
